<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-11-22 MainAnalysis.Rmd
Modularized fitting code by splitting different tasks into different functions. Note: Post-processing does not work yet because format of fitting output is different now (one row for each study & parameter and one column for each estimate metric -- vs. previous format of one row for each study & metric and one column for each parameter).
Working for 1-compartment model fits (though could still fine-tune starting values, need to diagnose NaN sds, etc.)

Calculate a limit of quantification (90% of lowest observation)
```{r, calc_loq, eval = TRUE}
cvt.data <- estimate_loq(cvt.data)
```

@@

```{r, set_file_timestamp, eval = TRUE}
THIS.DATE <- "20221115"
```

@@

```{r, run_invivoPKfit_1comp, eval = FALSE}
### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = cvt.data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = TRUE
))

write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)

write.csv(PK.fit.table.1comp[[2]], paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
```

```{r, run_invivoPKfit_2comp, eval = FALSE}
### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
    units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = TRUE
))
write.csv(PK.fit.table.2comp[[1]], paste("inst/ext/PK.fit.table.2comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
write.csv(PK.fit.table.2comp[[2]], paste("inst/ext/processed.2comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
```

>>>>

Calculate a limit of quantification (90% of lowest observation)

```{r, calc_loq, eval = TRUE}
cvt.data <- estimate_loq(cvt.data)
```

@@

```{r, set_file_timestamp, eval = TRUE}
THIS.DATE <- "2022_11_21"
```

@@

```{r, run_invivoPKfit_1comp, eval = FALSE}

devtools::load_all("invivopkfit")

### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = cvt.data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = FALSE
))

write.csv(PK.fit.table.1comp, paste("inst/ext/PK_fit_table_1comp_",THIS.DATE,".csv",sep=""), row.names = FALSE)

```{r, run_invivoPKfit_2comp, eval = FALSE}
### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
    units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = TRUE
))
write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
